---
output:
  html_document: default
  word_document: default
---
# Module 8 Assignment
### -- *Gregory Foster* --

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Step 1
#### Importing the Dataset with the read.table() function
```{r}
x= read.table("Assignment 6 Dataset.txt", header=TRUE, sep=",")
x
```

### Step 2
#### Using the plyr package to add a Grade.Average column to the data-frame

```{r}
library(plyr)
y = ddply(x, "Sex", transform, Grade.Average=mean(Grade))
y
```

### Step 3
#### Printing the updated dataset to a local file

```{r}
write.table(y, "Sorted_Average")
```

#### Converting the file to CSV with an additional function argument

```{r}
write.table(y, "Sorted_Average", sep=",")
```

### Step 4
#### Filtering the dataset to only include names that contain the letter "i", using a combination of the subset() and grepl() functions

```{r}
newx = subset(x, grepl("[iI]", x$Name))
newx
```

#### Writing the 'newx' subset data to a new local file

```{r}
write.table(newx,"DataSubset", sep=",")
```
